Teaching Low-Level Concurrency with \pebbles and \landslide

### 2016-08-26 sigcse-17/eval.tex
sigcse: finish off some intro todos; make a graph bigger
sigcse: refine eval description

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{p2-distribution.pdf}
	\caption{Distribution of thread library grades.}
	\label{fig:p2-distribution}
\end{figure}
We also collected the overall thread library grades to evaluate whether \landslide helps students achieve more during the project.
Figure~\ref{fig:p2-distribution} shows the distribution of these grades.
Compared to students from the same semesters who opted not to use \landslide,
those who did scored on average 3\% higher. % that's rough, buddy.
%
%However, to account for the possible bias for opting-out students being more at the bottom of the class
%on account of not enough free time to volunteer for \landslide,
However, the latter distribution is potentially biased towards struggling students
who lack enough free time to volunteer for \landslide.
To account for this, we also checked grades from prior semesters when \landslide was not available.
This distribution is indistiguishable from the experimental group,
suggesting that \landslide's benefit is largely offset by the time investment required.
%
In future work, we will streamline the user experience to help students fix as many concurrency bugs with a smaller time investment.

>>>>

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{p2-distribution-large.pdf}
	\caption{Distribution of thread library grades.}
	\label{fig:p2-distribution}
\end{figure}
We also collected the overall thread library grades to evaluate whether \landslide helps students achieve more during the project.
Figure~\ref{fig:p2-distribution} shows the distribution of these grades.
Compared to students from the same semesters who opted not to use \landslide,
those who did scored on average 3\% higher. % that's rough, buddy.
%
%However, to account for the possible bias for opting-out students being more at the bottom of the class
%on account of not enough free time to volunteer for \landslide,
However, the latter distribution is potentially biased towards struggling students
who lack enough free time to volunteer for \landslide.
To account for this, we also checked grades from prior semesters when \landslide was not available.
%This distribution is indistiguishable from the experimental group,
Although the minimum grade among the experimental group is 17\% higher than the minimum from prior semesters,
the middle 50\% of the distributions are quite similar,
suggesting that \landslide's benefit is largely offset by the time investment required.
%
In future work, we will streamline the user experience to help students fix as many concurrency bugs with a smaller time investment.
